\chapter{Categorization of Models}\label{ch:categorization}

The goal of this chapter is to categorize the available analytical and 
computational models into their salient characteristics according to the 
phenomena this modeling effort may address. For example, a table will be listed 
here detailing the phyical phenomena at work vs. the conceptual and 
mathematical models available, listed in order of complexity.

\input{./chapters/categorization/cat_table.tex}


\section{Fractures}

\subsection{Explicit Discrete Fracture Formulation}

This modeling formulation is complex and requires detailed knowledge of the 
candidate lithology. While an extensibility to include such a model will be 
retained in the repository system, it is well out of scope of the level of 
detail being sought by this nature of simulation. 

\subsection{Dual-Continuum Formulation}

The dual continuum formulation for either porosity or permeability allows a 
network of cracks to be  

It is one of the most widely employed models of fracture flow 
\cite{diodato_compendium_1994}.

\subsection{Discrete Fracture Network}
\subsection{Single Equivalent Continuum}

\subsection{Unsaturated or Multiphase Flow}
While some candidate repository geologies such as salt and granite are presumed 
to be unsaturated, the base case geology being modeled in this work is assumed 
to be saturated.


\section{Mixing}

\subsection{Precipitates}

\subsection{Dissolved Concentrations}



\section{Matter Dissolution}

\subsection{ Atomistic }

\subsection{ Molecular Dynamics } 

\subsection{ Staged }

Various stages of matter dissolution may include the initial attack, alteration, 
maturation, evolution, etc.

\subsection{ SWF/UFD/NEAMS data}

These will presumably give simplified constant rates. 


\section{Diffusion Coefficients}

\subsection{ Constant }

Tabulated.

\subsection{ Temperature Dependent : Arrhenius Relationship }

The Arrhenius relationship,

\begin{align}
  D &=D_0e^{-\frac{E_A}{RT}}
  \intertext{where}
  &D = \mbox{the diffusion coefficient}\\
  &D_0 = \mbox{the maximum diffusion coefficient}\\
  &E_A = \mbox{the ctivation energy of diffusion} [J \cdot kg^{-1}]\\
  &T = \mbox{is the temperature} [^\circ K]\\
  &R = \mbox{the ideal gas constant}[J \cdot \mbox{mol}^{-1} \cdot ^\circ 
  K^{-1}],\\
  \label{arrhenius}
\end{align}

gives the diffusion coefficient of solids as a function of temperature.


Gives D as a function of temperature and apparent activation energy of the 
medium.

\subsection{ Temperature Dependent : Stokes Einstein Relationship }

The Stokes-Einstein relationship,

\begin{align*}
  D(T) = \frac{k_B T}{6\pi \eta r}
\end{align*}

gives an equation for the diffusion coefficient in a fluid, as a function of T,  
the temperature of the surrounding medium, $k_B$, the Boltzmann constant, and 
$\eta$, the viscosity of the medium. This relationship is appropriate for 
media that have a low Reynolds number, 

\begin{align*}
  Re &= \frac{\rho v L}{\mu}\\
     \intertext{where}
     &\rho = \mbox{fluid density} [kg\cdot m{-3}]\\
     &v = \mbox{mean relative velocity of fluid} [m \cdot s^{-1}]<++>\\
     &L = \mbox{characteristic length of system} [m]\\
     &\mu = \mbox{dynamic fluid viscosity} [kg\cdot m^{-1} \cdot s{-1}]
\end{align*}

where viscous forces dominate. 


\subsection{ Concentration Dependent : ? }

Maybe there is a generally known functional form.


\section{Heat}

I'll be using the lumped parameter model for everything. Maybe linking to SINDA 
or the LLNL program. 
 

. . . 

