\chapter{Introduction}\label{ch:introduction}

% The scope of the work includes software and analysis.

The scope of this work includes implementation of Cyder, a software library of medium 
fidelity models to comprehensively represent various long-term disposal system 
concepts for nuclear material. This software library is integrated with the 
\Cyclus computational fuel cycle systems analysis platform in order to inform repository 
performance metrics with respect to candidate fuel cycle options. By abstraction 
of more detailed models, this work captures the dominant physics of 
radionuclide and heat transport phenomena affecting repository performance in 
various geologic media and as a function of arbitrary spent fuel composition. 

\section{Motivation} 

Thermal and radionuclide containment behavior of a geologic repository is a 
function of spent fuel and high level waste composition, which varies among 
alternative fuel cycles. For this reason, a generic disposal model capable of 
integration with a systems analysis framework is necessary to illuminate 
performance distinctions of candidate repository geologies, designs, and 
engineering components in the context of fuel cycle options. 

% There needs to be a system level approach to repository analysis that is both 
% modular and efficient.

The development of sustainable nuclear fuel cycles is a key challenge as the use 
of nuclear power expands domestically and internationally. While fuel cycle 
performance may be measured with respect to a variety of metrics, waste
management metrics are of particular importance to the goal of sustainability. 
Since disposal options are influenced by upstream fuel cycle decisions, a 
relevant analysis of potential geological disposal and engineered barrier 
solutions requires a system level approach that is both modular and efficient. 

% The approach must also be modular to support combinatorially complex 
% decision space 

As the merits of numerous combinatoric fuel cycle possibilities are 
investigated, a top-level simulation tool capable of modular substitution of 
various fuel cycle facility, repository, and engineered barrier components is 
needed. The modular waste package and repository models resulting from this work 
will assist in informing current technology choices, identifying important 
parameters contributing to key waste disposal metrics, and highlighting the most 
promising waste disposal combinations with respect to metrics chosen by
the user. Specifically, such models will support efforts underway in focusing 
domestic research and development priorities as well as computational tools 
under development that quantify these metrics and demonstrate the merits of 
different fuel cycle alternatives. 

% The modeling approach must be efficient in order for many scenarios to be 
% compared quickly

System level fuel cycle simulation tools must facilitate efficient sensitivity 
and uncertainty analyses as well as simulation of a wide range of fuel cycle 
alternatives.  Efficiency is achieved with models at a level of detail that 
successfully captures significant aspects of the underlying physics while 
achieving a calculation speed in accordance with use cases requiring repeated 
simulations.
Often termed abstraction, the process of simplifying while 
maintaining the salient features of the underlying physics is the method by 
which used fuel disposal system models were developed in this work. 

% The fuel cycle parameters that may be varied are numerous and coupled to the 
% back end.

Independent fuel cycle parameters of particular interest in fuel cycle systems 
analysis have historically been those related to the front end of the fuel cycle.
However, independent variables representing decisions concerning the back end
of the fuel cycle are of increasing interest as the United States further
investigates repository alternatives to Yucca Mountain.  Parameters such as the
repository geology, engineered barriers, appropriate loading strategies and
schedules are all independent variables up for debate. Due to the feedback 
implication of repository capacity and performance, these
parameters are coupled with decisions about the fuel cycle. 

% So we need a full systems analysis package, incorporating a repository. 

Thus, while independent parameters can be chosen and varied within a fuel cycle 
simulation, coupled parameters require full synthesis with a systems analysis 
code that appropriately determines the isotopic mass flows into the repository, 
their appropriate conditioning, densities, and other physical properties.  

\subsection{Future Fuel Cycle Options}

% DOE is interested in many fuel cycle options. 

Domestically, nuclear power expansion is motivated by the research, development, 
and demonstration roadmap being pursued by the United States Department of 
Energy Office of Nuclear Energy (DOE-NE), which seeks to ensure that nuclear 
energy remain a viable domestic energy option \cite{doe_nuclear_2010}. 

% DOE is considering 3 main options, each of which pose different waste 
% management challenges . . .

As the DOE-NE seeks to develop technologies and strategies to support a 
sustainable future for nuclear energy, various fuel cycle strategies and 
corresponding disposal system options are being considered.  Specifically, the 
domestic fuel cycle option space under current consideration is described in 
terms of three distinct fuel cycle categories with the monikers Once Through, 
Full Recycle, and Modified Open. Each category presents unique disposal system 
siting and design challenges. Systems analyses for evaluating these options must 
be undertaken in order to inform a national decision to deploy a comprehensive 
fuel cycle system by 2050 \cite{doe_nuclear_2010}. 

% Once through presents capacity issues . . . 

The Once-Through Cycle category includes fuel cycles similar to the continuation 
of the business as usual case in the United States.
Such fuel cycles neglect reprocessing and present challenges associated with 
high volumes of minimally treated spent fuel streams.  In a business as usual 
scenario, conventional power reactors comprise the majority of nuclear energy 
production and fuel takes a single pass through a reactor before it is 
classified as waste and disposed of. In the open cycle, no reprocessing is 
pursued, but research and development of advanced fuels seek to reduce waste 
volumes. Calculations from the Electric Power Research Institute corroborated by 
the \gls{US} \gls{DOE} in 2008 indicate that without an increase in the statutory 
capacity limit of the \gls{YMR}, continuation of the current Once Through fuel 
cycle will generate a volume of spent fuel that will necessitate
the siting of an additional federal geological repository to accommodate spent 
fuel \cite{kessler_room_2006, doe_report_2008}. 

% Full Recycle presents the issue of variable waste streams. . .

A Full Recycle option, on the other hand, requires the research, development, 
and deployment of partitioning, transmutation, and advanced reactor technology 
for the reprocessing of used nuclear fuel.  In this scheme, conventional 
once-through reactors will be phased out in favor of fast reactor and so called 
Generation IV reactor technologies, which demonstrate transmutation capacity and 
greater fuel efficiency. All fuel in the Full Recycle strategy will be 
reprocessed. It may be reprocessed using  an accelerator driven system or by 
cycling through an advanced fast reactor. Such fuel may undergo partitioning, 
the losses from which will require waste treatment and ultimate disposal in a 
repository. Thus, a repository under the Full Recycle scenario must support
a waste stream composition that is highly variable during transition periods as 
well as myriad waste forms and packaging associated with isolation of differing 
waste streams.

% Modified Open presents both problems. . . 

Finally, the Modified Open Cycle category of options includes a variety of fuel 
cycle options that fall between once through and fully closed. Advanced fuel 
cycles such as deep burn and small modular reactors will be considered within 
the Modified Open set of fuel cycle options as will partial recycle options.  
Partitioning and reprocessing strategies, however, will be limited to simplified 
chemical separations and volatilization under this scheme. This scheme presents
a dual challenge in which spent fuel volumes and composition will both vary 
dramatically among various possibilities within this scheme 
\cite{doe_nuclear_2010} .

% Various waste streams require various WFs and WPs 

Clearly, the myriad waste streams resulting from potential fuel cycles present 
an array of corresponding waste disposition, packaging, and engineered barrier 
system options. For a comprehensive analysis of the disposal system, dominant 
physics models must therefore be developed for each of these subcomponents.  Differing 
spent fuel composition, partitioning, transmutation, and chemical processing 
decisions upstream in the fuel cycle demand differing performance and loading 
requirements of waste forms and packaging. The capability to model thermal and 
radionuclide transport phenomena through vitrified glass as well 
as ceramic waste forms with with various loadings of arbitrary isotopic 
compositions is therefore required. This work has produced a repository model 
that meets this need. 

\subsection{Future Waste Disposal System Options}

% DOE is thinking about various geologies

In addition to reconsideration of the domestic fuel cycle policy, the uncertain 
future of the \gls{YMR} has driven the expansion of the option space of 
potential repository host geologies to include, at the very least, granite, 
clay/shale, salt, and deep borehole concepts \cite{nutt_used_2010}. 

% Various waste forms, packages, etc. are being considered.

In accordance with various fuel cycle options, corresponding waste form, waste 
package, and other engineered barrier systems are being considered.  
Specifically, current considerations include ceramic (e.g.  Uranium Oxide), 
glass (e.g.  borosilicate glasses), and metallic (e.g.  hydride fuels) waste 
forms. Waste packages may be copper, steel, or other alloys. Similarly, buffer 
and backfill materials vary from the crushed salt recommended for a salt 
repository to bentonite or concrete in other geologies. Therefore, a repository  
model capable of modular substitution of waste form models and data is
necessary to analyze the full option space.

% Various geologies, WFs, WPs, EBSs have various physics

The physical, hydrologic, and geochemical mechanisms that dictate 
radionuclide and heat transport vary between the geological and engineered 
containment systems in the domestic disposal system option space.  Therefore, 
in support of the system level simulation effort, models must be developed that 
capture the salient physics of these geological options and quantify associated 
disposal metrics.  Furthermore, in the same way that system level 
modularity facilitates analysis, so too does modular linkage between subcomponent 
process modules. These subcomponent models and the repository environmental model 
must achieve a cohesively integrated disposal system model such as is proposed by 
this work. 


\subsubsection{Thermal Modeling Needs}
% repository loading limits
% optimization of layout
% necessary decay cooling time before emplacement.
The decay heat from nuclear material generates a significant heat source within a 
repository. In order to arrive at loading strategies that comply with thermal 
limits in the engineered barrier system and the geological medium, a thermal 
modeling capability must be included in the repository model. Such a model is 
also necessary to inform material and hydrologic phenomena that affect 
radionuclide transport and are thermally coupled. 

Partitioning and transmutation of heat generating radionuclides within  
some fuel cycles will alter the heat evolution of the repository 
\cite{swift_applying_2010}. Thus, to distinguish  between the repository heat 
evolution associated with various fuel cycles involving partitioning and 
transmutation, a repository analysis model, must at the very least, 
capture the decay heat behavior of dominant heat contributors.  Plutonium, 
Americium, and their decay daughters dominate decay heat contribution within 
used nuclear fuels. Other contributing radionuclides include Cesium, Strontium, 
and Curium \cite{piet_which_2007}. 

Thermal limits within a used nuclear fuel disposal system are waste form, 
package, and geology dependent. The heat evolution of the repository 
constrains waste form loadings and package loadings as heat 
generated in the waste form is transported through the package. It 
also places requirements on the size, design, and loading strategy in a 
potential geological repository as that heat is deposited in the engineered 
barrier system and host geology.

Thermal limits of various waste forms have their technical basis in the 
temperature dependence of isolation integrity of the waste form. Waste form 
alteration, degradation, and dissolution behavior is a function of heat in 
addition to redox conditions and constrains loading
density within the waste form. 
 
Thermal limits of various engineered barrier systems similarly have a technical 
basis in the temperature dependent alteration, corrosion, degradation, and 
dissolution rates of the materials from whence they are constructed.  

Thermal limits of the geologic environment can be based on the mechanical 
integrity of the rock as well as mineralogical, hydrologic and geochemical 
phenomena. The isolating characteristics of a geological environment are most 
sensitive to hydrologic 
and geochemical effects of thermal loading. Thus, heat load constraints are 
typically chosen to control hydrologic and geochemical response to thermal 
loading. In the United States, current regulations necessitate thermal limits in 
order to passively steward the repository's hydrologic and geochemical integrity 
against radionuclide  release for the first 10,000 years of the repository.

The two heat load constraints that primarily determined the heat-based \gls{SNF} 
capacity limit in the Yucca Mountain Repository design, for example, are 
specific to unsaturated tuff. These are given here as an example of the type of 
regulatory constraints that this model captures for various geologies. 

The first Yucca Mountain heat load constraint is intended to promote constant 
drainage, thereby preventing episodic flow into waste package tunnels and
subsequent contaminated water flow through the repository. It requires that the 
minimum temperature in the tuff between drifts be no  more than the boiling 
temperature of water, which is $96^{\circ}C$ at the altitude in question. For a 
repository with homogeneous waste composition in parallel drifts, this constraint 
limits the temperature exactly halfway between adjacent drifts, where the 
temperature is at a minimum.

The second constraint is intended to prevent high rock temperatures that could 
induce fractures and alteration of the rock. It stated that no part 
of the rock reach a temperature above $200^{\circ}C$, and was effectively a 
limit on the temperature at the drift wall, where the rock temperature is a 
maximum.  

Analogous constraints for a broader set of possible geological environments 
depend on heat transport properties and geochemical behaviors of the rock matrix 
as well as its hydrologic state.  Such constraints affect the  
repository drift spacing, waste package spacing, and repository footprint among 
other parameters. 

%Clay repositories should have a ~70 degrees C limit, because temps higher than 
%100 degrees can cause irreversible minerological damage.
%From ANDRA:
%``In order to remain in an operational range in which phenomena are known and, 
%thus, reduce any damage to the argillite, the objective is to restrict 
%argillite temperature to these values. Basically, it means that the thermal 
%dimensioning of the cells and the architecture of the C waste repository zone 
%aim to restrict the temperature to 90°C at the interface “disposal cell – 
%argillite” and to ensure that the temperature will be below 70°C, in the 
%geological medium on the cell boundary, before a thousand years, which provides 
%a safety margin with respect to thermal effects.''

In addition to development of a concept of heat transport within the repository 
in order to meet heat load limitations, it is also necessary to model 
temperature gradients in the repository in  order to support modeling of 
thermally dependent hydrologic and material phenomena.  As mentioned above, 
waste form corrosion processes, waste form
dissolution rates, diffusion coefficients, and the mechanical integrity of 
engineered barriers and geologic environment are coupled with temperature 
behavior. 
Only a coarse time resolution is necessary to capture that coupling 
however, since time evolution of repository heat is
such that thermal coupling can typically be treated as quasi static for long 
time scales.
\cite{andra_argile:_2005}. %andra, clay, evaluation, page 195)

\subsubsection{Source Term Modeling Needs}

Domestically, the \gls{EPA} has defined a limit on  human 
exposure due to the repository. This regulation places important limitations on 
capacity, design, and loading techniques for repository concepts under 
consideration. Repository concepts developed in this work must therefore 
quantify radionuclide transport through the geological environment in order to 
calculate repository capacity and other metrics. 

The exposure limit set by the \gls{EPA} is based on a `reasonably maximally 
exposed individual.' For the \gls{YMR}, the limiting case is a person who lives, 
grows food, drinks water and breathes air 18 km downstream from the repository. 
The Yucca Mountain Repository \gls{EPA} regulations limit total dose from the 
repository to 15 mrem/yr, and limit dose from drinking water to 4 mrem/yr for 
the first 10,000 years. 
Predictions of that dose rate depend on an enormous variety of factors, most 
important of which is the primary pathway for release. In the \gls{YMR} primary 
pathway of radionuclides from an accidental release will be from cracking aged 
canisters. Subsequently, transport of the radionuclides to the water table 
requires that the radionuclides come in contact with water and travel through 
the rock to the water table. This results in contamination of drinking water 
downstream.  

Source term is a measure of the quantity of a radionuclide released into the 
environment whereas radiotoxicity is a measure of the hazardous effect of that 
particular radionuclide upon human ingestion or inhalation.  In particular, 
radiotoxicity is measured in terms of the volume of water dilution required to 
make it safe to ingest. Studies of source term and radiotoxicity therefore make 
probabilistic assessments of radionuclide release, transport, and human 
exposure.  

Importantly, due to the long time scale and intrinsic uncertainties required in 
such probabilistic assessments it is in general not advisable to base any 
maximum repository capacity estimates on source term. This is due to the fact 
that in order to give informative values for the risk associated with transport of 
particular radionuclides, for example, it is necessary to make highly uncertain  
predictions concerning waste form degradation, water flow, and other parameters 
during the long repository evolution time scale.  However, source term remains a 
pertinent metric for the comparison of alternative separations and fuel cycle
scenarios as it is a fundamental factor in the calculation of risk.
%The probabilistic nature of these assessments mean a direct dependence of 
%source term on repository capacity can be difficult to arrive at.  

Arriving at a generalized metric of probabilistic risk is fairly difficult. For 
example, the \gls{PEI} metric from Berkeley (ref.  
\cite{bouvier_comparison_2007}) is a multifaceted function of spent fuel 
composition, waste conditioning, vitrification method, and radionuclide 
transport through the repository walls and rock.  Also, it makes the assumption 
that the waste canisters have been breached at $t=0$. Furthermore, reported in 
$m^3$, PEI is a measure of radiotoxicity in the environment in the event of 
total breach. While informative, this model on its own does not completely 
determine a source-term limited maximum repository capacity.  Additional waste 
package failure and a dose pathway model must be incorporated into it.


\subsection{Domestic Research and Development Program}

The DOE-NE Fuel Cycle Technology (FCT) program has three groups of relevance to 
this effort: these are the \gls{UFD}, the \gls{SWF}, and \gls{FCO} (previously 
Systems Analysis) campaigns.  
The \gls{UFD} campaign is conducting the \gls{RDD} related to the storage, 
transportation, and disposal of radioactive wastes generated under both the 
current and potential advanced fuel cycles.  The SWF campaign is conducting 
\gls{RDD} on potential waste forms that could be used to effectively isolate the 
wastes that would be generated in advanced fuel cycles.  The \gls{SWF} and
\gls{UFD} campaigns are developing the fundamental tools and information base 
regarding the performance of waste forms and geologic disposal systems.  The 
\gls{FCO} campaign is developing the overall fuel cycle simulation tools and 
interfaces with the other FCT campaigns, including \gls{UFD}.  

This effort has interfaced with those campaigns to develop the higher level
dominant physics representations for use in fuel cycle system analysis tools.
Specifically, this work has leveraged conceptual framework development and
primary data collection underway within the Used Fuel Disposition Campaign as
well as work by Radel, Wilson, Bauer et. al. to model repository behavior as a
function of the contents of the waste \cite{radel_effect_2007}.  It then 
incorporated dominant physics process models into the \Cyclus computational 
fuel cycle analysis tool \cite{huff_cyclus:_2010} based on sensitivity analysis 
utilizing those detailed tools.

\section{Methodology} 

% Scope

In this work, concise dominant physics models suitable for system level fuel 
cycle codes were developed by comparison of analytical models with more 
detailed repository modeling efforts. The ultimate result of this work is a 
software library capable of assessing a wide range of combinations 
of fuel cycle alternatives, potential waste forms, repository design concepts, 
and geological media. 

% Selection of base set of subcomponents to model

Current candidate repository concepts have been investigated and reviewed here 
in order to arrive at a fundamental set of components to model. A preliminary 
set of combinations of fuel cycles, repository concepts, and geological 
environments has 
been chosen that fundamentally captures the domestic option space. 
Specifically, three candidate geologies and four corresponding repository 
concepts under consideration by the \gls{DOE} \gls{UFD} campaign have been 
chosen for modeling in this work. These have been implemented to interface
with \Cyclus simulations of a canonical set of potential fuel cycles within 
three broad candidate scenarios put forth by the \gls{US} \gls{DOE}.

% Review of available analytical models

A review and characterization of the physical mechanisms by which radionuclide 
and thermal transport take place within the materials and media under 
consideration was first undertaken. Potential analytical models to represent  
these phenomena were investigated and categorized within the literature review. 

% Review of available current detailed tools

A review and characterization of current detailed computational tools for
repository focused analysis was next conducted. Both international and domestic
repository modeling efforts were summarized within the literature review. Of 
these, candidate computational tools with which to perform abstraction and 
regression analyses were identified. Specifically, a suite of \gls{GDSM} tools 
under development by the \gls{DOE} \gls{UFD} campaign has informed radionuclide 
transport models and a pair of corresponding thermal analysis codes has 
informed the thermal models.
 
% For each component, abstraction of current tools and analytical models

This suite of subcomponent modules, appropriate for use within the \Cyclus fuel 
cycle simulator, has included the development of a robust architecture 
within the repository module that allows for interchangeable loading of 
system components.  Within the system components, dominant physics is 
modeled based on domain appropriate approximation of analytical models and 
supported by abstraction with the chosen \gls{GDSM} tools and thermal tools. 

% Abstraction = Analytic Solutions + Regression Approximation

These concise models are a combination of two components: 
semi-analytic mathematical models that represent a simplified description of 
the most important physical phenomena, and semi-empirical models that reproduce 
the results of detailed models.  By combining the complexity of the analytic 
models and regression against numerical experiments, variations were limited 
between two models for the same system.  Different approaches have been been 
compared in this work, with final modeling choices balancing the accuracy and 
efficiency of the possible implementations.  

% For example, Geology.

Specifically, these models focus on the hydrology and thermal 
physics that dominate radionuclide transport and heat response in candidate 
geologies as a function of radionuclide release and heat generation over long 
time scales. Dominant transport mechanism (advection or 
diffusion) and disposal site water chemistry (redox state) provide primary 
differentiation between the different geologic media under consideration. In 
addition, the concise models are capable of roughly adjusting release 
pathways according to the characteristics of the natural system (both the host 
geologic setting and the site in general) and the engineered system (such as package 
loading arrangements, tunnel spacing, and engineered barriers).

% Abstraction in repository environment

The abstraction process in the development of a geological environment model 
employs the comparison of semi-analytic thermal and hydrologic models and 
analytic regression of rich code results from more detailed models as well as 
existing empirical geologic data. Such results and data will be derived 
primarily from the \gls{UFD} campaign \glspl{GDSM} and data, as well as European 
efforts such as the RED-IMPACT assessment and \gls{ANDRA} Dossier efforts 
\cite{von_lensa_red-impact_2008, andra_argile:_2005, clayton_generic_2011} . 

% Example, heat from WPs along repo drifts.

%For example, analytic models and semi-empirical models are available (i.e.  
%specific temperature integrals in ref. \cite{li_methodology_2006} and the 
%specific temperature change index in ref. \cite{radel_effect_2007}) that 
%approximate thermal response from heat generation in waste packages as linear
%along repository drifts. These analyses arrive at a thermal evolution over time 
%at any location in the rock by superpositioning and integration. Subsequently, 
%their results can be converted easily into conventional line loading and areal 
%power density metrics.  Such analytic models will first be assessed to determine
%likely parameters upon which thermal response will rely (e.g. tunnel spacing, 
%radionuclide inventories, etc.).
%
% Regression.

Thereafter, a regression analysis concerning those parameters has been undertaken 
with available detailed models (e.g. 2D and 3D finite element thermal 
performance assessment codes) to further characterize the 
parametric dependence of thermal loading in a specific geologic environment.  

% Incorporation of empirical data

Finally, the thermal behavior of a repository model so developed depends on 
empirical data (e.g.  heat transfer coefficients, hydraulic conductivity).  
Representative values have been made available within the dominant 
physics models and rely on existing empirical data concerning the specific 
geologic environment being modeled (i.e. salt, clay/shale, and granite). 

% Abstraction for WFs, WPs, EBS, etc. will be the same

A similar process was followed for radionuclide transport models.  The 
abstraction process in the development of waste form, package, and engineered 
barrier system models will be analogous to the abstraction process of repository 
environment models. Concise models have resulted from employing the comparison of 
semi-analytic models of those systems with regression analysis of rich code in 
combination with existing empirical material data.

% Example, radionuclide release

%For instance, in the case of radionuclide release from waste packages, analytic 
%models of radionuclide release (e.g.  congruent or solubility limited) will 
%first be assessed to determine likely parameters upon which radionuclide release 
%will rely (e.g.  radionuclide concentration, water flow rates, etc.) 
%\cite{kawasaki_congruent_2004}.  Again, regression analysis concerning those 
%parameters will be undertaken with available detailed models to further 
%characterize the parametric dependence of radionuclide release from specific 
%waste packages.  Finally, the radionuclide release model so developed will 
%depend on empirical data (e.g. the waste form dissolution rate).  Determination 
%of representative values to make available within the dominant physics model 
%will rely on existing empirical data concerning the specific waste form  
%materials being modeled (i.e. long time scale extrapolations of known glass 
%degradation rates).  

% Coupling is confusing

Coupling effects between components were considered carefully.  In 
particular, given the important role of temperature in the system, thermal 
coupling between the models for the engineered system and the geologic system 
were considered. Thermal dependence of radionuclide release and transport as 
well as package degradation were analyzed to determine the 
magnitude of coupling effects in the system.

% Iterate

The full abstraction process was be iterated to achieve a balance between 
calculation speed and simulation detail. Model improvements during this stage 
sought a level of detail appropriate for informative comparison of subcomponents, but 
with sufficient speed to enable systems analysis. 

% Test using canonical data for those subcomponents

By varying input parameters and comparing with corresponding results from 
detailed tools, each model's behavior on its full parameter domain was 
validated.


\section{Outline}

% Summarize document

%A literature review, Chapter \ref{ch:litrev}, presents background material that organizes and 
%reports upon previous relevant work. First it summarizes the state of the art of 
%repository modeling integration within current systems analysis tools. It then 
%describes current domestic and international disposal system concepts and
%geologies.  Next, the literature review focuses upon current analytical and 
%computational modeling of radionuclide and heat transport through various waste 
%forms, engineered barrier systems, and geologies of interest.  It also 
%addresses previous efforts in generic geologic environment repository modeling in order to 
%categorize and characterize detailed computational models of radionuclide and 
%heat transport available for regression analysis.

% modeling paradigm

Chapter \ref{ch:paradigm} details the computational paradigm of the \Cyclus 
systems analysis platform and Cyder repository model which constitute this work. 
It describes the \Cyclus fuel cycle simulation context which drives fundamental 
Cyder design descisions. 

% methodology

Chapter \ref{ch:methodology} describes the radionuclide and heat transport 
models that were implemented. Models representing waste form, waste package, 
buffer, backfill, and engineered barrier componeents are defined by their 
interfaces and their relationships as interconnected modules, distinctly 
defined, but coupled. This modular paradigm allows exchange  of technological 
options (i.e. borosilicate glass and concrete waste forms) for comparison but 
also exchange of models for the same technological option with varying levels 
of detail.  

% Test Cases and Benchmarks

Chapter \ref{ch:demonstration} describes demonstration cases conducted to 
demonstrate radionuclide transport and thermal capacity analysis in Cyder. It 
also describes verification and validation procedures which benchmarked Cyder 
behavior against more detailed models.


Finally, in Chapter \ref{ch:conclusions}, contributions to the field and 
suggested future work are summarized. 

% Conclusions

Chapter \ref{ch:conclusions} will 

%%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%%
%%%%%%%% %%%%%%%% %%%% These chapters may be saved for the thesis . . .  
%%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% %%%%%%%% 

% Chapter \ref{ch:ebs} will adapt existing models and data to the development of 
% concise dominant physics waste form, waste package, and other engineered 
% barriers (i.e., bentonite or cementitious materials) models appropriate for 
% treatment of key radionuclides within the waste streams.  Material/barrier 
% degradation, radionuclide release, and radionuclide transport, and thermal 
% processes and effects will be included, as necessary, in the concise 
% representations that will be developed for subsequent use in the system-level 
% architecture. A range of waste forms, waste package materials, and other 
% engineered barrier materials (buffer, backfill) under consideration by the 
% DOE-NE FCT program (SWF and UFD campaigns) will be evaluated. The concise 
% dominant physics models will include appropriate load limiting factors of the 
% stabilizing medium and waste packaging including such as waste composition, 
% chemical form, and heat generation.
% 
% Chapter \ref{ch:extension} will discuss the future work necessary to extend 
% developed models to comprehensively cover the potential disposal system option 
% space. The path forward for extension of the geological base case model to 
% cover all five geologic concepts of interest (clay/shale, granite, salt, and 
% deep boreholes) will be discussed. Similarly, gaps in waste form and 
% engineered barrier system models and data will be addressed and a plan for 
% data and model coverage for that options space will be described.

