% Provide a brief description of the importance of the work (what problem it 
%   addresses/solves):

The development of sustainable nuclear fuel cycles is a key challenge as the 
use of nuclear power expands domestically and internationally.  Accordingly, 
the United States is simultaneously considering a number of domestic nuclear fuel 
cycle and geologic disposal options \cite{doe_strategy_2013}.  These decisions 
are technologically coupled by repository capacity. That is, 
radionuclide containment performance of a geologic repository is a function of 
spent fuel and high level waste composition, which varies among fuel cycle 
options. For this reason, a generic disposal model capable of integration 
with a systems analysis framework is necessary to illuminate performance 
distinctions of candidate repository geologies, designs, and engineering 
components in the context of fuel cycle options.  In answer to this need, Cyder 
integrates with the Cyclus computational fuel cycle systems analysis platform 
\cite{huff_cyder_2013,wilson_cyclus:_2012}. 


% The approach must also be modular to support combinatorially complex 
% decision space 

To support analysis of numerous combinatoric fuel cycle possibilities, a 
top-level simulation tool capable of modular substitution of various fuel cycle 
facility, repository, and engineered barrier components is needed. The modular 
waste package and repository models resulting from this work will assist in 
informing current technology choices, identifying important parameters 
contributing to key waste disposal metrics, and highlighting the most promising 
waste disposal combinations with respect to metrics chosen by the user. 

% Speed

A generic repository model appropriate for systems analysis must emphasize 
speed while providing modeling options at various levels of 
detail. Therefore, parameterized simulations and abstraction efforts conducted to develop 
the method described in this work sought to capture the dominant physics of 
thermal repository capacity assessment so that the Cyder disposal environment 
library could meet the simulation speed requirements of the Cyclus fuel cycle 
simulator.

% The modeling approach must be efficient in order for many scenarios to be 
% compared quickly

System level fuel cycle simulation tools must facilitate efficient sensitivity 
and uncertainty analyses as well as simulation of a wide range of fuel cycle 
alternatives.  Efficiency is achieved with models at a level of detail that 
successfully captures significant aspects of the underlying physics while 
achieving a calculation speed in accordance with use cases requiring repeated 
simulations.
Often termed abstraction, the process of simplifying while 
maintaining the salient features of the underlying physics is the method by 
which used fuel disposal system models were developed in this work. 

% The fuel cycle parameters that may be varied are numerous and coupled to the 
% back end.

Independent fuel cycle parameters of particular interest in fuel cycle systems 
analysis have historically been those related to the front end of the fuel 
cycle.
However, independent variables representing decisions concerning the back end
of the fuel cycle are of increasing interest as the United States further
investigates repository alternatives to Yucca Mountain.  Parameters such as
repository geology, engineered barriers, appropriate loading strategies and
schedules are all independent variables up for debate. Due to the feedback 
implication of repository capacity and performance, these
parameters are coupled with decisions about the fuel cycle. 

% So we need a full systems analysis package, incorporating a repository. 

Thus, while independent parameters can be chosen and varied within a fuel cycle 
simulation, coupled parameters require full synthesis with a systems analysis 
code that appropriately determines the isotopic mass flows into the repository, 
their appropriate conditioning, densities, and other physical properties.  

\subsection{Future Fuel Cycle Options}
\input{./chapters/intro/fuel_cycle_options}
\subsection{Future Waste Disposal System Options}
\input{./chapters/intro/waste_disposal_options}
\subsection{Domestic Research and Development Program}
\input{./chapters/intro/r_and_d}

