
By interfacing directly with the DOE-NE \gls{FCT} program, this work 
contributes directly to current fuel cycle analysis and disposal research 
underway domestically. The \gls{FCT} program has three groups of relevance to
this effort: these are the \gls{UFD}, the \gls{SWF}, and \gls{FCO} (previously
Systems Analysis) campaigns.  The \gls{UFD} campaign is conducting the
\gls{RDD} related to the storage, transportation, and disposal of radioactive
wastes generated under both the current and potential advanced fuel cycles.
The \gls{SWF} campaign is conducting \gls{RD} on potential advanced separations
technologies including associated waste forms that could be used to effectively
isolate the wastes that would be generated in advanced fuel cycles.  The
\gls{SWF} and \gls{UFD} campaigns are developing the fundamental tools and
information base regarding the performance of waste forms and geologic disposal
systems.  The \gls{FCO} campaign is developing the overall fuel cycle
simulation tools and interfaces with the other FCT campaigns, including
\gls{UFD}.  

This effort has interfaced with those campaigns to develop the higher level 
dominant physics representations for use in fuel cycle system analysis tools.  
Specifically, this work has leveraged conceptual framework development and 
primary data collection underway within \gls{UFD}.  It has also benefited from 
University-laboratory collaboration via work by Radel, Wilson, Bauer et. al. to 
model repository behavior as a function of the contents of the waste 
\cite{radel_effect_2007}.  
