I am grateful to a number of extraordinary professors and colleagues at the 
Universities of Wisconsin and Chicago, as well as the national laboratories, 
who have inspired and encouraged me. My committee members, Dr. Jean~M.~Bahr, Dr.  
Michael~L.~Corradini, Dr. Douglass~L.~Henderson, Dr. W.~Mark~Nutt, Dr.  
Paul~P.H.~Wilson, and Dr. Robert~J.~Witt, were especially supportive in this 
endeavor.  

Among them, I am especially indebted to my advisor, Professor~Wilson, 
for his indispensible technical and practical guidance. He has been a dedicated 
ally, always generous with analytical perspectives, far-ranging enthusiasm, 
and deep concern for the professional and personal well being of his students. 
I am similarly grateful to my laboratory advisor, Dr.~Nutt, an 
outstanding mentor who has provided critical direction and resources for the 
work at hand. Special gratitude also goes to Professor~Bahr, whose 
expertise and detailed feedback were of exceptional value.  

So too, my colleagues Kyle~M.~Oliver, Matthew~J.~Gidden and Robert~W.~Carlsen 
have been essential in the success of the \Cyclus project as well the growth of 
my collaborative abilities. I thank Alexander Bara for dedicating a summer to 
starting the STC database. Additionally, all confidence I have in 
these results is owed to software practices inspired by my friends among The 
Hacker Within and Software Carpentry. At the risk of neglecting someone, I must 
thank Greg Wilson, Animal1, Wolfman, Slayer, Scopz, Nico,  BlackBeard, 
BlondeBeard, and RedBeard. I owe my sanity to Denia Djoki\'{c}.

This work was carried out in the \gls{CNERG} of the University of Wisconsin - 
Madison's \gls{EP} Department and the \gls{UFD} Campaign at \gls{ANL}. This 
work is supported by the U.S. Department of Energy, Basic Energy Sciences, 
Office of Nuclear Energy, under contract \# DE-AC02-06CH11357.
