\section{Radionuclide Transport Base Cases}\label{sec:nuclide_base_cases}
%Also, for most of 5.2, you need to make the case that the single result you show 
%is representative!!  I think that's easy, but needs to be done.  Essentially, 
%you need to make the case that for real isotopes, the same model will be 
%invoked with real parameters, so that these normalized (relative?) parameters 
%are representative of all cases.
In the following base cases, basic transport behavior for aphysical 
parameterizations demonstrate the successful collective behavior of the modular 
components in a \Cyder repository.

\subsection{Basic Transport and Containment Problem Specification}
Basic transport and containment base cases were conducted to verify the 
fundamental behavior of all the radionuclide transport models at each component 
interface. These integration tests neglected thermal transport and capacity 
estimation to simplify the results.  

The problem design includes the following : 
\begin{itemize}
\item{A source facility providing one waste stream per time step}
\item{An initial capacity of five 1 kg waste streams (in most cases)}
\item{Waste form Components each accepting 1 waste stream} 
\item{Corresponding waste package Components, one per waste form}
\item{A buffer Component}
\item{A far field Component}
\end{itemize}

\subsubsection{Degradation Rate Model}
The Degradation Rate model should not release contaminants if the degradation 
rate is 0. If the degradation rate is nonzero, however, and a fixed maximum 
transport mode is selected, contaminants should become available immediately to 
the adjacent components, traveling across the interfaces entirely at each 
time step. 

To observe these behaviors, four simulations were run to demonstrate that, for 
the fixed maximum transfer mode, total 
containment resulted from a degradation rate of 0 and that congruent release 
resulted from nonzero degradation rates. 
In the four following simulations, a waste form with 1 kg is introduced to the repository once 
per time step for the first five time steps. Those five waste packages are 
placed into a single buffer component, which is contained by a single far field 
component. All are represented by the Degratdation Rate Model. 

Further destails of these verification 
cases can be found in Table \ref{tab:dr_base}. The 0 degradation rate component was 
different for each of the four cases. This resulted in total containment at the 
Waste Form, Waste Package, Buffer, and Far Field interfaces respectively. 
Results of these base cases can be found in Figures 

\ref{fig:drIwf5} through \ref{fig:drIVff0}.
\FloatBarrier
\input{./chapters/demonstration/base/dr_base_tab}
\input{./chapters/demonstration/base/dr_base_fig}
\FloatBarrier

\subsubsection{Mixed Cell Model}
The Mixed Cell model behaves similarly to the Degradation Rate model, when 
sorption and solubility limitation in that model are disabled (as in Figures 
\ref{fig:mcI} through \ref{fig:mcIff0}). When they are enabled, however, the 
system is expected to demonstrate sorption limited and solubility limited 
transport as in Figures \ref{fig:mcIIIall} through \ref{fig:mcII}. The extent 
to which sorption and solubility limitation meet expectations is addressed in 
this base case.  

Dual and single parameter verification cases were run to explore the effects of 
sorption and solubility limitation both separately and together.  Results from 
two of these base cases can be found in Figures \ref{fig:mcI} through 
\ref{fig:mcII}.
The fixed maximum transport mode was use between mixed cell components for speed 
and clarity of results.

In the two following simulations, a waste form with 1 kg is introduced to the repository once 
per time step for the first five time steps. Those five waste packages are 
placed into a single buffer component, which is contained by a single far field 
component. All are represented by the Mixed Cell Model. Each component except 
the far field has a degradation rate of 0.1 per time step.

\input{./chapters/demonstration/base/mc_base_fig}
\FloatBarrier

\subsubsection{Lumped Parameter Model}

The Lumped Parameter model, with its three formulations (Exponential Model, 
Dispersion Model, and Piston flow Model) is not expected to receive 
contaminants if the porosity or advective velocity are zero. Otherwise, 
contaminants are expected to  become available to the adjacent components 
according to the functional forms of the formulations. 

To observe the behaviors of each of the three formulations and to demonstrate 
full containment in cases where it is expected, simulations were run to 
investigate the impact of using various models. Results of these base cases can be found in Figures 
\ref{fig:lpBegin} through \ref{fig:lpEnd}.

In the three following simulations, a waste form with 1 kg is introduced to the repository once 
per time step for the first five time steps. Those five waste packages are 
placed into a single buffer component, which is contained by a single far field 
component. All are represented by the Lumped Parameter Model.

\input{./chapters/demonstration/base/lp_base_fig}

The transit time that parameterizes these models could be based on radioactive 
tracer experiments in the laboratory. Figures \ref{fig:lp_t_t_begin} 
and \ref{fig:lp_t_t_end} demonstrate the dependence of the resulting transport on 
transit time parameteriztion. These profiles demonstrate the trends seen in the 
analytical results demonstrated in Maloszewski and Zuber 
\cite{maloszewski_lumped_1996}.

\input{./chapters/demonstration/base/lp_t_t_fig}

\subsubsection{One Dimensional Permeable Porous Medium Model}
The One Dimensional PPM Model does not release contaminants if the porosity is 
zero or if both the reference diffusivity and advective velocity are zero. 
Otherwise, however, contaminants are expected to  become available to the adjacent 
components according to the analytical form of the solution. The solution is 
only valid for advection and dispersion values within a realistic range, and 
the model accordingly can only be demonstrated for a very slow transport case. 

To observe the behavior of the solution and to demonstrate full containment in 
cases where it is expected, simulations were run with each component represented 
by a One Dimensional PPM Model, which uses an implicit mass transfer mode. An 
example simulation, with reference dispersion coefficient at $1\times 10^{-12}$ 
m/s$^2$ and advective velocity of $1\times 10^{-15}$ m/yr 
In this simulation, a waste form with 1000 kg 
is loaded into a waste package. That waste package is the only package in the 
buffer and far field components that contain it.

\input{./chapters/demonstration/base/1d_base_fig}
\FloatBarrier
is shown in Figure \ref{fig:odall}. 
